Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-01-16 RR_manuscript/Draft_RR.Rmd
:construction: - begin fixing error from figure (WIP)

documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf:
    number_sections: true
header-includes:
  - \usepackage{cleveref}
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
library(tidyverse)
library(patchwork)
```

@@

```{r forkingPaths, echo=FALSE, fig.cap="Illustrations of the analytical flexibility associated with acoustic analyses. (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b. The words "another is highlighted by the green box"; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch", fig.dim = c(6, 2)}

knitr::include_graphics("/RR_manuscript/Draft_RR_files/figure-latex/ForkingPaths.png")

>>>>

documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf:
    number_sections: true
    latex_engine: xelatex
header-includes:
  - \usepackage{cleveref}
---

```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = here::here())
library("papaja")
r_refs("r-references.bib")
library(tidyverse)
library(patchwork)
```

@@

```{r forkingPaths, echo=FALSE, fig.cap="Illustrations of the analytical flexibility associated with acoustic analyses. (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b. The words \"another is highlighted by the green box\"; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch", fig.dim = c(6, 2)}

knitr::include_graphics("./RR_manuscript/img/ForkingPaths.png")
